Abstract Plots

### 2021-07-27 Abstract.Rmd
Tweaked some graphs.

#provide predictions and labels
MMR.pred <- prediction(MMR.ROC$MMR, MMR.ROC$truthMMR)
MMR.perf <- performance(MMR.pred, measure = "tpr", x.measure = "fpr")
tob.pred <- prediction(tob.ROC$Tobacco, tob.ROC$truthTob)
tob.perf <- performance(tob.pred, measure = "tpr", x.measure = "fpr")
plot(MMR.perf, colorize=TRUE, print.cutoffs.at=0.5, text.adj=c(-0.2,1.7),
     main = "ROC curve of classifier", lty = 2) #ROC
plot(tob.perf, colorize=TRUE, print.cutoffs.at=0.5, text.adj=c(-0.2,1.7), 
     add = TRUE, lty = 3)
abline(a=0, b= 1)
legend("bottom", c("Signature 6 with FFPE noise", "Signature 4 with FFPE noise"),
       lty = 2:3)
```

@@

```{r}
num.mut=1000
probabilities.MMR <- vector(mode = "list", length = 99)
truth.MMR <- vector(mode = "list", length = 99)

for (x in seq(10, num.mut-1, by = 10)){
  sample.ffpe <- create_signature_sample_vector(ffpe.sig, x)
  ffpe.truth <- rep("FFPE", x)
  sample.sig6 <- create_signature_sample_vector(cosmic.sig6, num.mut-x)
  sig6.truth <- rep("MMR", num.mut-x)
  test <- get_classification_df(list(sample.sig6, sample.ffpe), c("MMR","FFPE"),
                                list(cosmic.sig6, ffpe.sig))
  classification <- test %>%
    mutate(trueBinary = ifelse(truth == "MMR",1,0))

  probabilities.MMR[[x/10]] <- classification$MMR
  truth.MMR[[x/10]] <- classification$trueBinary
}
```

```{r}
num.mut=1000
probabilities.tob <- vector(mode = "list", length = 99)
truth.tob <- vector(mode = "list", length = 99)

for (x in seq(10, num.mut-1, by = 10)){
  sample.ffpe <- create_signature_sample_vector(ffpe.sig, x)
  ffpe.truth <- rep("FFPE", x)
  sample.sig4 <- create_signature_sample_vector(cosmic.sig4, num.mut-x)
  sig4.truth <- rep("Tobacco", num.mut-x)
  test <- get_classification_df(list(sample.sig4, sample.ffpe), c("Tobacco","FFPE"),
                                list(cosmic.sig4, ffpe.sig))
  classification <- test %>%
    mutate(trueBinary = ifelse(truth == "Tobacco",1,0))

  probabilities.tob[[x/10]] <- classification$Tobacco
  truth.tob[[x/10]] <- classification$trueBinary
}
```

@@

```{r}
AVG.sens.MMR <- vector(mode = "list", length = 99)

@@

```{r}
AVG.sens.tob <- vector(mode = "list", length = 99)

@@

```{r}
sensitivity = append(sens.MMR.vec, sens.tob.vec)
signature.sens = append(rep("MMR", length(sens.MMR.vec)),
                        rep("Tobacco", length(sens.tob.vec)))
dilution = append(1:99, 1:99)
sens.df <- data.frame(dilution, sensitivity, signature.sens)

ggplot(data = sens.df, mapping = aes(x = dilution, 
                                     y = sensitivity, 
                                     color = signature.sens)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Sensitivity as a function of FFPE noise",
       x = "Percent of FFPE noise in samples",
       y = "Sensitivity value",
       color = "True signal") +
  coord_cartesian(ylim = c(0,1))
```

@@

```{r}
AVG.spec.MMR <- vector(mode = "list", length = 99)

for(iteration in 1:20){
  spec.MMR <- performance(test.MMR, measure = "spec")

@@

```{r}
AVG.spec.tob <- vector(mode = "list", length = 99)

for (iteration in 1:20){
  spec.tob <- performance(test.tob, measure = "spec")

@@

```{r}
specificity = append(spec.MMR.vec, spec.tob.vec)
signature.spec = append(rep("MMR", length(sens.MMR.vec)),
                        rep("Tobacco", length(spec.tob.vec)))
dilution = append(1:99, 1:99)
spec.df <- data.frame(dilution, specificity, signature.spec)

ggplot(data = spec.df, mapping = aes(x = dilution, 
                                     y = specificity, 
                                     color = signature.sens)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Specificity as a function of FFPE noise",
       x = "Percent of FFPE noise in samples",
       y = "Specificity value",
       color = "True signal") +
  coord_cartesian(ylim = c(0,1))
```

@@

ggplot(data = sens.df, mapping = aes(x = dilution, 
                                     y = sensitivity, 
                                     color = signature.sens)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Specificity as a function of mutational load",
       x = "Number of mutations in each sample",
       y = "Specificity value") +
  coord_cartesian(ylim = c(0,1))
```

@@

ggplot(data = spec.df, mapping = aes(x = dilution, 
                                     y = specificity, 
                                     color = signature.spec)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Specificity as a function of mutational load",
       x = "Number of mutations in each sample",
       y = "Specificity value") +
  coord_cartesian(ylim = c(0,1))
```

>>>>

#provide predictions and labels
MMR.pred <- prediction(MMR.ROC$MMR, MMR.ROC$truthMMR)
MMR.perf <- performance(MMR.pred, measure = "tpr", x.measure = "fpr")
tob.pred <- prediction(tob.ROC$Tobacco, tob.ROC$truthTob)
tob.perf <- performance(tob.pred, measure = "tpr", x.measure = "fpr")
plot(MMR.perf, print.cutoffs.at=0.5, text.adj=c(-0.2,1.7),
     main = "ROC curve of classifier", lty = 2) #ROC
plot(tob.perf, print.cutoffs.at=0.5, text.adj=c(-0.2,1.7), 
     add = TRUE, lty = 3)
abline(a=0, b= 1)
legend("bottom", c("Signature 6 with FFPE noise", "Signature 4 with FFPE noise"),
       lty = 2:3)
```

@@

```{r}
num.mut = 1000
step = seq(50, 950, by = 50)
```

```{r}
probabilities.MMR <- vector(mode = "list", length = length(step))
truth.MMR <- vector(mode = "list", length = length (step))

for (x in 1:length(step)){
  sample.ffpe <- create_signature_sample_vector(ffpe.sig, step[x])
  ffpe.truth <- rep("FFPE", step[x])
  sample.sig6 <- create_signature_sample_vector(cosmic.sig6, num.mut-step[x])
  sig6.truth <- rep("MMR", num.mut-step[x])
  test <- get_classification_df(list(sample.sig6, sample.ffpe), c("MMR","FFPE"),
                                list(cosmic.sig6, ffpe.sig))
  classification <- test %>%
    mutate(trueBinary = ifelse(truth == "MMR",1,0))

  probabilities.MMR[[x]] <- classification$MMR
  truth.MMR[[x]] <- classification$trueBinary
}
```

```{r}
probabilities.tob <- vector(mode = "list", length = length(step))
truth.tob <- vector(mode = "list", length = length(step))

for (x in 1:length(step)){
  sample.ffpe <- create_signature_sample_vector(ffpe.sig, step[x])
  ffpe.truth <- rep("FFPE", step[x])
  sample.sig4 <- create_signature_sample_vector(cosmic.sig4, num.mut-step[x])
  sig4.truth <- rep("Tobacco", num.mut-step[x])
  test <- get_classification_df(list(sample.sig4, sample.ffpe), c("Tobacco","FFPE"),
                                list(cosmic.sig4, ffpe.sig))
  classification <- test %>%
    mutate(trueBinary = ifelse(truth == "Tobacco",1,0))

  probabilities.tob[[x]] <- classification$Tobacco
  truth.tob[[x]] <- classification$trueBinary
}
```

@@

```{r}
AVG.sens.MMR <- vector(mode = "list", length =length(step))

@@

@@

```{r}
sensitivity = append(sens.MMR.vec, sens.tob.vec)
signature.sens = append(rep("MMR", length(sens.MMR.vec)),
                        rep("Tobacco", length(sens.tob.vec)))
dilution = append(step/10, step/10)
sens.df <- data.frame(dilution, sensitivity, signature.sens)

ggplot(data = sens.df, mapping = aes(x = dilution, 
                                     y = sensitivity, 
                                     color = signature.sens)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Sensitivity as a function of FFPE noise",
       x = "Percent of FFPE noise in samples",
       y = "Sensitivity value",
       color = "True signal") +
  coord_cartesian(xlim = c(0,100), ylim = c(0,1))
```

@@

for(iteration in 1:50){
  spec.MMR <- performance(test.MMR, measure = "spec")

@@

for (iteration in 1:50){
  spec.tob <- performance(test.tob, measure = "spec")

@@

```{r}
specificity = append(spec.MMR.vec, spec.tob.vec)
signature.spec = append(rep("MMR", length(sens.MMR.vec)),
                        rep("Tobacco", length(spec.tob.vec)))
dilution = append(step/10, step/10)
spec.df <- data.frame(dilution, specificity, signature.spec)

ggplot(data = spec.df, mapping = aes(x = dilution, 
                                     y = specificity, 
                                     color = signature.sens)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Specificity as a function of FFPE noise",
       x = "Percent of FFPE noise in samples",
       y = "Specificity value",
       color = "True signal") +
  coord_cartesian(xlim = c(0,100), ylim = c(0,1))
```

@@

ggplot(data = sens.df, mapping = aes(x = dilution, 
                                     y = sensitivity, 
                                     color = signature.sens)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Sensitivity as a function of mutational load",
       x = "Number of mutations in each sample",
       y = "Sensitivity value",
       color = "True signal") +
  coord_cartesian(ylim = c(0,1))
```

@@

ggplot(data = spec.df, mapping = aes(x = dilution, 
                                     y = specificity, 
                                     color = signature.spec)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Specificity as a function of mutational load",
       x = "Number of mutations in each sample",
       y = "Specificity value",
       color = "True signal") +
  coord_cartesian(ylim = c(0,1))
```
